European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-11 manuscript/manuscript.qmd
fix 2nd para

Our empirical analysis yields several key findings that challenge conventional wisdom about IMF decision-making. First, European influence demonstrates a broader and more consistent association with favourable lending outcomes than previously recognised. Countries with stronger ties to major European powers—the United Kingdom, France, and Germany—receive significantly larger loans relative to GDP, participate more frequently in IMF programmes, and enjoy higher approval rates for new lending arrangements. These effects are statistically significant and substantively meaningful, suggesting that European actors wield considerable institutional influence over the Fund's core lending functions.

>>>>

Our empirical analysis yields several key findings that challenge conventional wisdom about IMF decision-making. First, European influence demonstrates a broader and more consistent association with favourable lending outcomes than previously recognised. Countries with stronger ties to major European powers，namely, the United Kingdom, France, and Germany, receive significantly larger loans relative to GDP, participate more frequently in IMF programmes, and enjoy higher approval rates for new lending arrangements. These effects are statistically significant and substantively meaningful, suggesting that European actors wield considerable institutional influence over the Fund's core lending functions.
